### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   new file:   paper.ver07.pdf

The fourth one, \emph{pretrained model based joint text classification and NER model}. 
We choose the work from \cite{chen2019bert} as our baseline system, which utilizes a strong RoBERTa-large model to jointly train two losses.
Our SFC framework is also conveniently supportive of extra NER loss that in stage 1 a fourth task with a NER loss is trivially derived based on the output states from a pretrained model.

@@

\subsubsection*{Supportive of extra NER task}
Many previous work shows joint training with a NER loss improves the intent classification task as well, observed again in our baselines and SFCs in Table \ref{tbe:addtional ner experiments}.
We choose the state-of-the-art RoBERTa-large model with NER loss as a strong baseline.

We can see that our joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percentage points on average. 
This indicates that the fusion of classification and similarity models can even works better than fusing with additional NER information under few-shot chatbot scenario.

Moreover, the adding NER loss to joint SFC further achieves improvement of 1.66 percentage points over RoBERTa with NER loss baseline. 
Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint SFC with NER loss achieves a bigger improvement of 2.8 percentage points on average.

>>>>

The fourth one, \emph{pretrained model based joint text classification and NER model}. 
We choose the work from \cite{chen2019bert} as our baseline system, which utilizes a strong RoBERTa-large model to jointly train two losses.

@@

\subsubsection*{Supportive of extra NER task}
Many previous work shows joint training with a NER task improves the intent classification task as well, observed again in our baselines and SFCs in Table \ref{tbe:addtional ner experiments}.
Our SFC systems set the weight of the fourth NER task as 0.25 throughout this part.

We can see that our joint SFC without a NER task still outperforms RoBERTa baseline with a NER task by 0.86 percentage points on average. 
This indicates that the fusion of classification and similarity models can even works better than fusing with additional NER information under few-shot chatbot scenario.

Moreover, the adding NER task to joint SFC further achieves improvement of 1.66 percentage points over RoBERTa baseline with a NER task. 
Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint SFC with a NER task achieves a bigger improvement of 2.8 percentage points on average.

### 2021-05-18 chatbot_classification/03.emnlp_2021/introduction.tex
modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   new file:   paper.ver07.pdf

Despite plenty of success of these two methodologies, they still have some limitations in this task especially when data is insufficient.
Regarding the \emph{text classification model}, it learns a function that directly maps an input query into its expected label.
Its training requires data in the form of a pair of a query and a task dependent label. 
It is quite hard to adopt labeled data from other domains, as their label definitions are often incompatible to each other. 
Though we can use some data augmentation methods to alleviate the paucity of data, e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the case that our labeled data is very insufficient.
Regarding the \emph{similarity model}, the foremost advantage is it does not pose any restriction on the label definition of user intents, but aims to learn a function that measure how similar of two sentences are. 
Then in the intent detection task, we are only concerned which labeled query is the most similar one to the current input, and then use its label as the output.
This results in a possibility that even though the labeled data in current domain is scarce, we may borrow additional data from another domain to help enhance the similarity model to make a better intent prediction.
Nevertheless, just as every coin has two sides, the high flexibility of similarity model leads to its worse performance compared to a classification model, because its training loss differs from a classification loss corresponding to the intent detection goal.
More, it requires an auxiliary model to narrow down candidate labeled queries to speed up the calculation, which makes it slow in the speed and tricky in the auxiliary model selection.

>>>>

Despite plenty of success of these two methodologies, they still have some limitations in this task especially when data is insufficient.

Regarding the \emph{text classification model}, it learns a function that directly maps an input query into its expected label.
The training requires data in the form of a pair of a query and a task dependent label. 
Yet it is quite hard to adopt existent labeled data from other domains, since their label definitions are often incompatible to each other. 
Though we can use some data augmentation methods to alleviate the paucity of data, e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the cases that labeled data is rather insufficient.

Regarding the \emph{similarity model}, the foremost advantage is it does not pose any restriction on the label definition of user intents, but aims to learn a function that measure how similar of two sentences are. 
Then in the intent detection task, we are only concerned which labeled query is the most similar to the current input, and then use its label as the output.
This results in a possibility that even though the labeled data in current domain is scarce, we may borrow additional data from another domain to help enhance the similarity model to make a better intent prediction.
Nevertheless, just as every coin has two sides, the high flexibility of similarity model leads to its worse performance compared to a classification model, as it is not trained towards the goal in the intent detection task which is actually a 0-1 loss minimization.
More, it requires an auxiliary model to narrow down candidate class labels to speed up the similarity calculation next step, and this auxiliary model should be of a good balance in precision and recall.
